\documentclass[a4paper, 14pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\title{\bf Assignment 01}
\author{Xugang Zhou \\ Fangzhou Yang \\ Yuwen Chen}
\pagestyle{fancy}
\lhead{{\bf Distributed Algorithms}\\WS 2013/14, Prof. Dr.-Ing. Jan Richling}
\rhead{Assignmen 01}
\renewcommand{\headrulewidth}{0.4pt}
\begin{document}
\begin{titlepage}
\begin{center}
\vfill
\textsc{\LARGE Distributed Algorithms}\\[1.5cm]
\textsc{\Large }\\[0.5cm]

\HRule \\[0.4cm]
{\huge \bfseries Assignment 01}\\[0.4cm]
\HRule \\[1.5cm]
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Group Members:}\\
Xugang \textsc{Zhou}\\
Fangzhou \textsc{Yang}\\
Yuwen \textsc{Chen}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Tutor:} \\
Daniel \textsc{Graff}\\
\end{flushright}
\end{minipage}
\vfill
{\large \today}\\
\end{center}
\end{titlepage}
\thispagestyle{fancy}
\section{Warming Up}
\begin{itemize}
\item[a.] The difference between a distributed system and a parallel
  system is that: {\bf A parallel system has a common physical memnory,
  while computers in a distributed system loosely connect to each
  other and communicate through message exchange.}
\item[b.] A complicated distributed system can be used to check
  whether an algorithm is reliable. For example, we can use
  a complicated distributed system to model the real network which can
  be used to test a certain mechanism in the network. With more
  complexity, there's a greater change that there would appear a bug.
\item[c.] Difference between {\it Synchronous System Model} and {\it
    Asynchronous System Model} is the maximum duration of an action or
  a message. In {\it Synchronous System Model}, they are assumed
  restricted or known. But in {\it Asynchronous System Model}, their
  limits are unknown.
On the other hand, {\it Atom Model} is similar to {\it Synchronous
  System Model}, but its actions are timeless.
\end{itemize}
\section{Topologies}
The number of possible spanning trees that can be generated from a d
dimension Hypercube is:\\
\begin{equation}
c(C(d)) = \prod_{k=2}^{d}(2k)^{d \choose k}
\end{equation}
In order to execute the broadcast withour interfering each
other. Besides simple broadcast information, we let each node (node U,
e.x.) send a node sets $U_{send}$ to the broadcasted node (node V
e.x.). So that:\\
\begin{equation}
V_{receive} = U_{send} = U_{receive} \cup neighbour(U)
\end{equation}
Which means V won't broadcast the information to the node set
$V_{receive}$. \\
\section{Flooding with Achnowledgments}
\section{Echo Algorithm}
\end{document}